Peer influences in air travel behavior: A social autoregressive analysis

### 2015-04-10 article/article.Rmd
Added reference and cleaned up document.

---
title: "Peer influences in air travel behavior: A social autoregressive analysis"
author: Gregory S. Macfarlane, Thomas A. Wall, Bingling Zhang, and Kari E. Watkins
bibliography: bibliography/bibliography.bib
csl: bibliography/elsevier-harvard.csl 
output:
  html_document:
    fig_caption: yes
    number_sections: yes
---
```{r setup}
library(knitr) # nice output tables

@@

```{r distance_from_atlanta}
cities <- read.csv("data/PRIVATEDATA/geocode/geocoded_datatables/allcities.csv")%>%
  tbl_df()

@@

**Direct Friendship**
This schema defines a simple binary matrix where a cell is nonzero if  and  are
friends. Specifically,

@@

**Mutual Friendship**
This schema defines a matrix where the cell value is the number of friends  and
have in common (as in Gilbert & Karahalios 2009; He et al. 2012),

@@

**Network Overlap**
This schema defines a matrix where the cell value is the relative overlap of
each pair’s social network (as in Adamic & Adar 2003),

>>>>

---
title: "Peer influences in air travel behavior: A social autoregressive analysis"
author: Gregory S. Macfarlane, Thomas A. Wall, Bingling Zhang, and Kari E. Watkins
bibliography: bibliography/bibliography.bib
csl: bibliography/elsevier-harvard.csl 
output:
  html_document:
    fig_caption: yes
    theme: journal
    number_sections: yes
---
```{r setup}
library(knitr) # nice output tables

@@

```{r distance_from_atlanta, eval=FALSE}
cities <- read.csv("data/PRIVATEDATA/geocode/geocoded_datatables/allcities.csv")%>%
  tbl_df()

@@

**Direct Friendship**
This schema defines a simple binary matrix where a cell is nonzero if $i$ and 
$j$ are friends. Specifically,

@@

**Mutual Friendship**
This schema defines a matrix where the cell value is the number of friends $i$
and $j$ have in common [as in @Gilbert2009; @He2012],

@@

**Network Overlap**
This schema defines a matrix where the cell value is the relative overlap of
each pair’s social network [as in @Adamic2003],
